Proposal full title \\ Proposal Acronym

### 2001-10-08 drafts/IST/PartA.tex
removed cvs conflicts header
svn path=/trunk/; revision=1487

mailing lists, Project management... But although there are
many hosting facilities around the world, no software package is designed to
setup and maintain a set of machines dedicated to this purpose. The NAME
project will provide a generic solution that can be used and adapted by all of
them.
NAME will of course provide the same services as current facilities but
will focus an the ease of configuration and installation that all current ones
lack.

@@

680 characters...

@@

The NAME project aims at developping a complete hosting facility. It composed
of two subprojects. \\
The first one is the NAME project that will be a next generation hosting
facility. It will provide a web frontend to a number of tools are now mandatory
for software development (user/groups rights management, bug tracking, mailing
lists and forums...). The main idea between its design is to make it
transparently distributed. At each step of its development, we will focus on
the ease of installation and configuration.
The second one is the "CoopX" project that will provide a generic description of
an hosting facility. With that tool we want to allow different kind of facility
to communicate each other. It will help to develop tools to facilitate
migrations between hosting facilities.
\\ 800 chars need some check and some other stuff:w

@@

of the solution will allow the validation and testing of each milestone.
% 450
%COOPX
\subsection*{Milestones and expected result (max 500 characters)}
%%% HELP HELP
\end{document}

>>>>

mailing lists, Project management... But although there are many hosting
facilities around the world, no software package is designed to setup and
maintain a set of machines dedicated to this purpose. \\ 
The NAME project will provide a generic solution that can be used and adapted
by all of them.  NAME will of course provide the same services as current
facilities but will focus an the ease of configuration and installation that
all current ones lack. \\
NAME will also provide support for internationalization to help dissemination
and adoption in European countries for non english speakers.\\ Finally NAME
will introduce support for cooperation in hosting platforms, that will be a
first step to the creation of networks of hosting facilities. 

@@

989 characters... (846 non white) \\

@@

The NAME project aims at developping a complete hosting facility. It is 
composed of two parts. \\
The first one will be a next generation easy to install and international
hosting facility. It will provide a web frontend to a number of tools now 
mandatory for software development (user/groups rights management, bug tracking, mailing lists and forums...). 
The main idea between its design is to make it transparently distributed.
At each step of its development, we will focus on the ease of installation and configuration.  will also provide support for internationalization to help dissemination and adoption in European countries for non english speakers.\\
The second one will provide a generic description of
an hosting facility. With that tool we want to allow different kinds of facility
to communicate with each other. It will help to develop tools to facilitate
migrations between hosting facilities. This part is more oriented on data formats and tools to exchange informations between hosting facilities. It may
be released as an individual package from the first part.\\
\\ 1087/924 chars need some check and some other stuff

@@

of the solution will allow the validation and testing of each milestone.\\
Our primary goal is to build a set of packages that is easy to
install on a virgin machine or a machine already used for other
purposes. 
Although we have in mind that the set of packages produced could be used for
multiple purposes, our focus will be on development hosting facilities. 
created network (for example savannah or sourceforge) ;

% 450
%COOPX
\subsection*{Milestones and expected result (max 500 characters)}
%%% HELP HELP
\section*{A4 Cost Summary}
%% will look at that later
\rotatebox{90}{
\begin{tabular}{c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
Participant Role(CO/P) & Participant Number & Linked to Contractor No &
Participant Short Name & Number of Person - Months & Personnel Costs &
Durable Equipment & Consumables & Travel and subsitence & Computing &
External assistance & Other Costs & Knowledge protection on Costs & 
Overhead Costs & Total Costs & Requested Contribution from the Commision &
Eligibility (Y/No)\\
\end{tabular}
}
\end{document}
